### 2019-03-22 ms.tex
Bring rest of ms up to date with new cv schemes.

Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for both data types.
We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We then compare results from the joint model with those made using (a) a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and (b) a model created using prevalence point-survey data similar to the model used by Bhatt \emph{et al.}\cite{bhatt2015effect}.
Each set of three models is applied to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.
We find that the joint model performs better than the polygon-only model in cases where predictions are needed far from the location of the data or when there are few polygon incidence datapoints available for learning relationships between covariates and malaria risk.

@@

% Random results
% Maps, reasonable for both
% MAE performance.

For the random cross-validation experiments, the polygon-only model had the lowest mean absolute error, with respect to predicting incidence, for Indonesia and Senegal (Table~\ref{table1}).
Incidence in Madagascar was best predicted by the joint model.
However, the difference between the two models in Indonesia was small.
Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter}A, C and E.
From the scatter plots it can be seen that the point-only model is strongly biased, overestimating incidence in Indonesia and Madagascar and underestimating incidence in Senegal.

@@

The benchmark points-only model had the lowest weighted MAE between observed and predicted prevalence for both Senegal and  Madagascar while the wighted MAE was the same for all three models in Indonesia (Table~\ref{table1}).
The more pertinent comparison is whether the addition of the prevalence data improves the ability of the polygon-only models to predict pixel level prevalence.
However, weighted MAE was unchanged between the polygon-only model and the joint model for Indonesia, Senegal or Madagascar.
Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{randompredobsscatter} B, D and F.
All models show poor predictive performance in Indonesia and Senegal with none of the models being able to accurately predict the large number of points with zero prevalence.
The predictions in Madagascar are better though the large number of surveys with measured prevalence of zero are still problematic.

Maps of the Indonesian input data and predictions (Figures~\ref{predobsmapidn}A and B) indicate that the broad spatial patterns of malaria incidence were recovered with areas in Papua, Borneo and Suluwasi being estimated as relatively high risk.
Similarly, input data and predictions (Figures~\ref{predobsmapsen}A and B) for Senegal show broad agreement with malaria incidence being higher in the South.

% Further results. Accuracy or recall of Sen. Correlation for some?

% Spatial results
% Maps, reasonable for india, get's broad pattern even far away from data. Poor for SEN, wrong overall pattern. Different covariates.
% MAE performance.

For the spatial cross-validation experiments, the joint model had the best predictive performance for both Senegal and Madagascar.
The polygon-only model again had the lowest mean absolute error between observed and predicted incidence for Indonesia (Table~\ref{table2}).
Scatter plots of the out-of-sample predictions can be seen in Figures~\ref{spatialpredobsscatter}A, C and E.

Again, the benchmark points-only model had the lowest weighted MAE between spatially cross-validated observed and predicted prevalence for Senegal.
However, for Indonesia, both the polygon-model and the joint model marginally outperformed the points-only model. 
However, scatter plots of the out-of-sample predictions show that there is almost no correlation between observed and predicted values (Figures~\ref{randompredobsscatter} B, D and F).
For Senegal, the joint model (0.065) had the lowest weighted MAE for predicted prevalence though this was again marginal (points-only 0.069, polygons-only 0.066).
Again the survey-points with prevalence of zero were difficult to correctly predict.

Maps of the Indonesian input data and spatially out-of-sample predictions (Figures~\ref{predobsmapidn}A and C) suggest the that the broad spatial patterns were once again recovered.
This acceptable performance is notable given the very large areas held out-of-sample (Fig~\ref{fig:cv_spatial}).
For example, the whole of Papua and West Papua the the East are held out in a single fold.
In contrast the predictions for Senegal do not match those observed in the input data (Figures~\ref{predobsmapsen}A and C).

@@

The polygon-only model and the joint model seem to be fairly well calibrated (Table~\ref{table3}).
The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
The points-only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.

With respect to uncertainty in polygon incidence predictions, the polygon-only model and joint model were similar; adding the prevalence point-survey data sometimes improved coverage and sometimes made it worse.
However, with respect to uncertainty in prevalence point-survey predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
Coverage improved in the random cross-validation in Indonesia and Madagascar and spatial cross-validation in Madagascar and marginally improved in the spatial cross-validation in Senegal.
In the remaining two cases, adding prevalence point-surveys did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation Senegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.

@@

We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapsen}).
With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both Senegal and Madagascar but not Indonesia (Table~\ref{table2}).

We used held-out prevalence point-surveys to measure how well the models predicted within-polygon, pixel-level malaria risk.
Given the poor performance by all models, including the points-only model (Figures~\ref{randompredobsscatter} and \ref{spatialpredobsscatter}), particularly in Indonesia and Senegal these results must be interpreted with care.
% Add sample size, comparisons etc.
In particular, a majority of the prevalence point-surveys in all countries found zero malaria infections (though the age standardisation moves these to slightly non-zero values) and small sample sizes were common in the Senegal and Indonesia data.
Given the poor performance of the points-only model, it is not useful to interpret these results as a direct measure of a models ability to predict within-polygon, pixel level risk.
Instead we can, with care, interpret the relative performance of models.
In five cases, the polygon-only and joint model had the same predictive performance on the prevalence point-surveys.
In only one cases, the joint model was marginally better.
Therefore we conclude that the joint model is no better than the polygon-only model at predicting within-polygon, pixel-level malaria risk.

% Discuss and interpret. Generalise

The joint model improved the prediction of polygon incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
The two countries where the joint model performed best in the spatial cross-validation scheme are the two countries with the least data.
The joint model seemed to perform comparatively well in the cases where predictions had little information from the random field and when there is little data to estimate regression parameters.
Far-from-data predictions are particularly susceptible to overfitting.
Given the simple linear model, adding prevalence point-surveys may protect against overfitting by increasing the amount of data available.
Alternatively, the improved perforamance could be because a model that learns from two datasets, on different scales, with different biases, is also less likely to overfit.

In contrast, the joint model does not in general improve on the polygon-only model in the random cross-validation scheme.
A noticable element of this scheme was that locations where polygon incidence data was removed for validation could still potentially have prevalence point-survey data.
Figure~\ref{fig:cv_random} implies that this situation is the norm.
Yet this spatial information did not improve performance in Indonesia or Senegal.

% Clear benefits, when some areas have polygon and some have PR.
%   Where?

There are two main reasons why a model fitted jointly on prevalence point-surveys and polygon incidence data may perform worse than a polygon-only mode.
Firstly, the data are on difference scales.
Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, seasonality and age-structure are not constant \cite{cameron2015defining, battle2015defining,reiner2015seasonality}.
In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
The second aspect of prevalence point-survey data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.

For a model to be robust to shortcomings in the prevalence-incidence relationship from \cite{cameron2015defining}, future models could be more flexible in the way they use this relationship.
This could be by estimating the parameters of the polynomial jointly with the rest of the model.
Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not be used by the incidence level model.
This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.

For the model to handle noisy or biased prevalence point-surveys, the modeller can control the iid random effect on the point-surveys, $w_i$. 
Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e. based on the differences in prevalence surveys within the same pixel).
Weakening this prior will allow the iid effect to explain more of the prevalence point-survey variation which both reduces the potential statistical power gained by adding the point-surveys but also reduces the effects of biased or noisy estimates.

There are large potential benefits to models that combine data in the context of large scale studies over multiple countries.
In these cases there is often different data types in different countries and being able to make malaria estimates of the countries together increases spatial coverage and statistical power.
Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data. 
In these regions, fitting a model on just the prevalence point-surveys requires predictions far away from the survey locations whlie fitting a model just on the polygon incidence data will be underpowered. 
However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.

In order to specifically compare the affects of combining the data types, we have aimed to keep the models fitted here as simple as possible.
However, a number of improvements could be made.
Data from multiple years are available for many countries.
Simply combining data collected at different times is not recommended as malaria incidence is changing rapidly.
However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive \cite{bhatt2015effect, taylor2017continuous}.
This is an avenue of work that should be pursued.
Furthermore, it has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
A number of methods could be used to include non-linear effects of covariates and interactions into the model.
Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines \cite{sissoko2017temporal, sewe2017using, hundessa2018projecting}, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
These are computational expensive without careful approximations via variational Bayes or other approximations.
Again these models need a lot of data and careful regularisation for good predictive performance.

>>>>

Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for both data types.
We relate the differing malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We then compare results from the joint model with those made using a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
Both models are fitted to data from Indonesia, Senegal and Madagascar to provide a set of case studies with disparate geographic settings and levels of malaria endemicity.

@@

% Random cv

Under the random cross-validation scheme, the joint model performed best in Indonesia and Madagascar while the polygon only model performed best in Senegal (Table \ref{table1}).
The differences were relatively small in all three countries.
This lack of strong differences is highlighted by the fact that there are no clear differences in scatter plots of observed and predicted data (Figure \ref{randompredobspolyfacet}).

% spatial 1

Under the spatial a cross-validation scheme, the polygon only model performed best in Indonesia and Senegal while the joint model performed best in Madagascar (Table \ref{table1}).
In contrast to the random cross-validation results, the differences between models is quite strong.
Furthermore, notable difference can be seen in the scattor plots of observed and predicted values (Figure \ref{spatial2predobspolyfacet}).
In Indonesia it can be seen the the joint model is more strongly biased at low incidence values with many data points being overpredicted.
In Senegal the predictions from the joint model do not appear biased but are often far from the observed value.
However, the joint model clearly performs better in Madagascar with the polygon only model particularly struggling to predict high incidence observations correctly.

% spatial b

Under the spatial b cross-validation scheme, in which the prevalence data are spatially withheld, the polygon model again performs the best in Indonesia and Senegal while the joint model performs best in Madagascar (Table \ref{table1}).
The bias in the low incidence observations in Indonesia is no longer present (Figure \ref{spatial1predobspolyfacet}).
In Indonesia and Senegal the joint model performs worse in the spatial a cross-validation than in the spatial b cross-validation scheme.
Given that more data is being witheld in spatial b this implies that the bias caused by the prevalence points is so severe that models perform worse with this spatial information than with just information from the covariates.

@@

@@

The polygon-only model and the joint model seem to be fairly well calibrated (Table~\ref{table3}).
The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.54 and 0.9.
However, in most cases coverage was between 0.7 and 0.8 implying the models were a little overconfident in their predictions.

@@

We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
